---
title: "Getting Started with AtlasMaker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AtlasMaker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

```{r setup}
library(AtlasMaker)
library(shiny)
```

Provided datasets for this vignette include:

counties_NY                                 
points_campgrounds                          
points_parks                                
points_watchsites                           
roads_ny_interstate  

```{r}
load("~/ds_projects/AtlasMaker/data/vignette_data_prepped.rdata")
```


# Creating Lists for Map Tab Creation

## Tab 1, Flowering Plants

```{r}
## for tab 1: flowering plants-------------
polys_flowering_plants <- list(
    list(
        name = 'flowering_plants',
        data = flowering_plants,
        label = 'name',
        fill = 'fill_value'
    )
)

points_flowering_plants <- list(
    list(
        name = 'points_parks',
        data = points_parks,
        long = 'long',
        lat = 'lat',
        label = 'label'
    )
)

```



## Tabs 2-4



```{r}
# 2. Create lists per tab/theme-----------------


## for tab 2-------------
polys_birds <- list(
  list(
    name = 'birds',
    data = birds,
    label = 'name',
    fill = 'fill_value'
  )
)

lines_birds <- list(
  list(
    name = 'ny_interstates',
    data = roads_ny_interstate
  )
)

points_birds <- list(
  list(
    name = 'points_watchsites',
    data = points_watchsites,
    long = 'long',
    lat = 'lat',
    label = 'label'
  ),
  list(
    name = 'points_campgrounds',
    data = points_campgrounds,
    long = 'long',
    lat = 'lat',
    label = 'label'
  )
)

## for tab 3-------------

polys_amph_rept <- list(
  list(
    name = 'amphibians',
    data = amphibians,
    label = 'name',
    fill = 'fill_value'
  ),
  list(
    name = 'reptiles',
    data = reptiles,
    label = 'label',
    fill = 'fill_value'
  )
)

points_amp_rept <- list(
  list(
    name = 'points_parks',
    data = points_parks,
    long = 'long',
    lat = 'lat',
    label = 'label'
  ),
  list(
    name = 'points_campgrounds',
    data = points_campgrounds,
    long = 'long',
    lat = 'lat',
    label = 'label'

  )
)

## for tab 4-------------
# All Polygons
polys_all <- list(
  list(
    name = 'flowering_plants',
    data = flowering_plants,
    label = 'name',
    fill = 'fill_value'
  ),
  list(
    name = 'birds',
    data = birds,
    label = 'name',
    fill = 'fill_value'
  ),
  list(
    name = 'amphibians',
    data = amphibians,
    label = 'name',
    fill = 'fill_value'
  ),
  list(
    name = 'reptiles',
    data = reptiles,
    label = 'label',
    fill = 'fill_value'
  )
)

# All Points
points_all <- list(
  list(
    name = 'points_parks',
    data = points_parks,
    long = 'long',
    lat = 'lat',
    label = 'label'
  ),
  list(
    name = 'points_campgrounds',
    data = points_campgrounds,
    long = 'long',
    lat = 'lat',
    label = 'label'
  )
)


```


# Plug into Shiny UI/Server

## Set Standard Shiny UI

```{r}
# 3. Set ui/layout --------
ui <- fluidPage(
    titlePanel("AtlasMaker Demo Map (v0.9)"),
        mainPanel(
            tabsetPanel(
                tabPanel('Flowering Plants', map_UI('flowering_plants')),
                tabPanel('Birds', map_UI('birds')),
                tabPanel('Amphibians & Reptiles', map_UI('amph_rept')),
                tabPanel("All", map_UI("allthegoods"))
            )

        )
    )
```


## Set Standard Shiny Server, with AtlasMaker::map_server

Create 1 map_server per theme/tab with as few/little 'arguments' as you need ------

see 'colors' section of Leaflet guide for options to pass in for colors/palettes
rstudio.github.io/leaflet/colors.html

pass in any base layer from the link below into 'map_base_theme'
http://leaflet-extras.github.io/leaflet-providers/preview/index.html



```{r}
server <- function(input, output) {
    map_server("flowering_plants",
               polygons = polys_flowering_plants,
               polylines = NULL,
               points = points_flowering_plants,
               poly_palette = 'RdPu',
               point_color = 'brown'
               )
    map_server("birds",
             polygons = polys_birds,
             polylines = lines_birds,
             points = points_birds,
             map_base_theme = 'Stamen.Watercolor',
             poly_palette = 'YlGn',
             point_color = '#ffa500',
             polyline_color = "#964b00"
              )
    map_server("amph_rept",
             polygons = polys_amph_rept,
             polylines = NULL,
             points = points_amp_rept,
             map_base_theme = 'Esri.WorldImagery',
             poly_palette = 'Greens',
             point_color = "black"
            )
    map_server("allthegoods",
               polygons = polys_all,
               polylines = NULL,
               points = points_all
              )
}
```

# Run the App

```{r}
# Run the application
shinyApp(ui = ui, server = server)
```







